---
title: "Alcohol vs Seat choice"
author: "Abel Jacobo Perez"
date: "09-14-2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??
$h_0$ There is no difference an alcohal consumption  based on where one sits in class
$h_A$ There is a difference of alcohal consumption based on where one sits in class
## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  the Box plot shows that people who sit in tha back tend to drink alcohal at a higher average level compared to those who sit in middle or the front.
  
  The front of the class seems to drink the least with the middle of the class drinking slightly more then the front but less then the back of the class.
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
## Conclusions


