---
title: "Alcohol vs Seat choice"
author: "Abel Jacobo Perez"
date: "09-14-2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??
$h_0$ There is no difference an alcohal consumption  based on where one sits in class
$h_A$ There is a difference of alcohal consumption based on where one sits in class
## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  the Box plot shows that people who sit in the back tend to drink alcohol at a higher average level compared to those who sit in middle or the front.
  
  The front of the class seems to drink the least with the middle of the class drinking slightly more then the front but less then the back of the class.
  
  
  the front and middle show little difference in alcohol consumption.
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

 There is little to no difference between those who sit in the front to middle and there is a huge diference between the front to middle and the back;the back drinks alot. The front to middle drink less.

## Numerical Summarys

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

The average student who sits in the back drinks significangtly more at 8.55 while those in front and middle drink significantly less at levels of 1.78(front) and 3.33(middle)

## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The P value is too low.


```{r}
plot(TukeyHSD(model1))
```
 The tukeu shows that there the middle to back drinks significantly more then the middle to back.
 
First we got the P value of 0.000116, so we conclude we reject the $h_0$;there is a difference bewteen where you sit in class and your alcohol consumption


 I reject the Null hypothesis. There is a difference in alcohol consumption depending on where you sit in the classroom.
 
##Conclusions 

 The people who sit in the back of the class room drink significantly more then those who sit in the middle or front of the class,we reject the Null hypothesis ; there is an association between where you sit and how much you drink. Also the P value is to low so there is little to no chance to replicate the results.
 

